Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-08 MCQMC2022ChallengesQMCSoftwareArticle.tex
SC: refine

We draw on our collective experiences as
members of the academic QMC community in the, developers of open-source and commercial scientific software, and users of a wide range of scientific software as research scientists or data scientists. Many of the insights that we have gained have come through our development of the Guaranteeed Automatic Integration Library (GAIL)~\cite{ChoEtal22a} in MATLAB and the Quasi-Monte Carlo Python library (QMCPy)~ \cite{QMCPy2020a}.   \FJHNote{Sou-Cheng, not sure what this means.} \SCComment{Fred, more elaboration here: In particular, QMCPy is not just a QMC software containing our own algorithms; from the outset, it is designed to serve as a middleware framework, allowing users to tap into a collection of QMC libraries originally written in various languages by different researchers at different times. Using object-oriented design, QMCPy specifies a few  extensible high-level mathematical objects essential in multiple integration. Developers of other (Q)MC software could easily extend these objects to incorporate their existing or working algorithms by a combination of mechanism: object inheritance; Python package inclusion; direct code translation; interfaces to compiled C or Java libraries. Hence QMCPy has been able to provide access to an increasing number of well established (Q)MC algorithmic or application software such as QRNG~\cite{}, MLMC~\cite{}, GAIL~\cite{}, UM-Bridge~\cite{}.}

>>>>

We draw on our collective experiences as
members of the academic QMC community in the, developers of open-source and commercial scientific software, and users of a wide range of scientific software as research scientists or data scientists. Many of the insights that we have gained have come through our development of the Guaranteeed Automatic Integration Library (GAIL)~\cite{ChoEtal22a} in MATLAB and the Quasi-Monte Carlo Python library (QMCPy)~ \cite{QMCPy2020a}.   \FJHNote{Sou-Cheng, not sure what this means.} \SCComment{Fred, more elaboration here, but maybe it fits better in Section 3: In particular, QMCPy is not just a QMC software containing our own algorithms; from the outset, it is designed to serve as a middleware framework, allowing users to tap into a collection of QMC libraries originally written in various languages by different researchers at different times. Using object-oriented design, QMCPy specifies a few  extensible high-level mathematical objects essential in multiple integration (see Sect.\ \ref{CDHJS_sec:integrated}). Developers of other (Q)MC software could easily extend these objects to incorporate their existing or working algorithms by a combination of mechanism: object inheritance; Python package inclusion; direct code translation; interfaces to compiled C or Java libraries. Hence QMCPy has been able to provide access to an increasing number of well established (Q)MC algorithmic or application software such as QRNG~\cite{}, MLMC~\cite{}, GAIL~\cite{}, UM-Bridge~\cite{}.}
